---
output:
  md_document:
    variant: markdown_github
---

# cloclimer

R package to standardise statistical analyses of time series in the CoClime project.

## Installation

The package is not on CRAN. Install it with

```{r install, eval=FALSE}
# if needed
install.packages("devtools")
# then
devtools::install_github("jiho/coclimer")
```


## Usage

Load the package

```{r load}
library("coclimer")
```

A test dataset is included in the package, containing the concentration of *Ostreopsis ovata* in two forms and environemental variables. Read more about it with

```{r help, eval=F}
?ost
```

Make it available and inspect it with

```{r inspect}
data(ost)
head(ost)
```

Your data should be made to look the same: a `date` column, columns for species concentrations/abundances, columns for environmental variables.

Plot the data

```{r plot}
# full time series
plot_multi(ost, benthic:planktonic)
plot_multi(ost, benthic:planktonic, trans="sqrt")
# seasonal view
plot_seasonal(ost, benthic:planktonic, trans="sqrt")
```

Compute standardised yearly statistics

```{r stats}
# for benthic concentration
yearly_stats(ost$date, ost$benthic, bloom_threshold=200000)
```

Inspect correlations of abundance with environmental variables

```{r corr}
library("tidyverse")
d <- filter(ost, benthic>0)
correlate(sqrt(d$benthic), select(d, chla:temperature), n=3)
```

Read more in the help of the functions.
